\chapter*{Bibliography}
\addcontentsline{toc}{chapter}{Bibliography}

\begin{enumerate}

\item\label{bib:fontes2026}
R.~Fontes,
\textbf{Operator Factorization Beyond Hilbert Spaces: Representability Obstructions and Leibniz Defects for Stable L\'evy Processes},
Quijotic Research, 2026.
DOI: \texttt{10.5281/zenodo.18625711}.

\item\label{bib:fontes2026hilbert}
R.~Fontes,
\textbf{The Operator Derivative in Continuous Stochastic Calculus},
Quijotic Research, 2026.
(Companion Hilbert-space formalization: \texttt{OperatorDerivative.lean}, $\sim$5200 lines, 0 sorry.)

\item\label{bib:nualart2006}
D.~Nualart,
\textbf{The Malliavin Calculus and Related Topics},
2nd ed., Springer, 2006.

\item\label{bib:applebaum2009}
D.~Applebaum,
\textbf{L\'evy Processes and Stochastic Calculus},
2nd ed., Cambridge University Press, 2009.

\item\label{bib:sato1999}
K.~Sato,
\textbf{L\'evy Processes and Infinitely Divisible Distributions},
Cambridge University Press, 1999.

\item\label{bib:peskir2006}
G.~Peskir and A.~Shiryaev,
\textbf{Optimal Stopping and Free-Boundary Problems},
Birkh\"auser, 2006.

\item\label{bib:nourdin2012}
I.~Nourdin and G.~Peccati,
\textbf{Normal Approximations with Malliavin Calculus: From Stein's Method to Universality},
Cambridge University Press, 2012.

\item\label{bib:dimasi1994}
G.~Di~Masi, Yu.~Kabanov, and W.~Runggaldier,
\textbf{Mean-variance hedging of options on stocks with Markov volatilities},
\textit{Theory of Probability and its Applications}, 39(1):172--182, 1994.

\item\label{bib:sole2007}
J.~L.~Sol\'e, F.~Utzet, and J.~Vives,
\textbf{Canonical L\'evy process and Malliavin calculus},
\textit{Stochastic Processes and their Applications}, 117(2):165--187, 2007.

\item\label{bib:last2011}
G.~Last and M.~Penrose,
\textbf{Poisson process Fock space representation, chaos expansion and covariance inequalities},
\textit{Probability Theory and Related Fields}, 150(3--4):663--690, 2011.

\item\label{bib:mathlib}
The Mathlib Community,
\textbf{Mathlib4: The Lean 4 Mathematical Library},
\texttt{https://github.com/leanprover-community/mathlib4}, 2024--2026.

\end{enumerate}
